---
title: "Orange Tree Study"
title2: "MSDS 6303 Case Study 2 Question 2"
author: "Joseph Denney, Timothy McWilliams and Laurie Harris"
date: "April 24, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Introduction

There is a data file available in R which contains circumference measurements for five orange trees.  These measurements are identified by age of the tree in days from a baseline date.  This analysis will show the circumference measurement changes over a timeframe of 1582 days beginning on December 31, 1968 and a final measurement on day 1582 or May 1, 1973.

##Data Gathering
The data can be obtained very simply by calling the dataframe, Orange, from the R console.
```{r,code=readLines('Orange_Data.R'),eval = TRUE}
```

##Data Analysis
We would like to understand more about the circumferences of each tree therefore we will compute the mean and median circumferences from the measurement data.
```{r,code=readLines('Orange_Calc.R'),eval = TRUE}
```

##Graphical Examination
To demonstrate the differences in circumferences over the timeframe, we will present two plots that show the data for each tree.  The first plot shows the circumference change over time for each tree.  The second plot shows the range of circumference change as separate boxplots for each tree.  
```{r,code=readLines('Orange_Plots.R'),eval = TRUE}
```

##Conclusion
In each of the displays, we notice that tree number 4 has the highest mean and median circumferences and tree number 3 has the lowest mean and median circumferences.  The range circumferences of trees 1 and 3 appear to be similar, on a smaller scale, while trees 2 and 4 appear to share similar, larger circumference ranges.
